|

### 2024-08-10 doc/paper.qmd
em3

### Discretion in Reported Earnings: The Magnitude of Accruals (EM3)
EM3 is a measure that obtains the degree of discretion that insiders exercise when reporting earnings, particularly when it comes to misstating a firm’s economic performance. It focuses on the magnitude of accruals as a proxy for earnings management. Insiders can use accruals to overstate or understate earnings, thereby achieving certain financial targets or presenting a skewed view of the firm’s performance.

@@

The replicated table shows some similarities with the original table by @Leuz_2003 in that . These findings are in line with valuation ***theory*** that .

However, the patterns are less clear in the replicated table (in particular ), which stands in contrast to @Leuz_2003.

@@

>>>>

### Discretion in Reported Earnings: The Magnitude of Accruals (EM3)
EM3 is a measure that obtains the degree of discretion that insiders exercise when reporting earnings, particularly when it comes to misstating a firm’s economic performance. It focuses on the magnitude of accruals as a proxy for earnings management. Insiders can use accruals to overstate or understate earnings, thereby achieving certain financial targets or presenting a skewed view of the firm’s performance. Higher scores of EM3 indicate more earnings management, as larger magnitudes of accruals relative to cash flow from operations suggest greater discretion in financial reporting.

@@

##The replicated table shows some similarities with the original table by @Leuz_2003 in that . These findings are in line with valuation ***theory*** that .

##However, the patterns are less clear in the replicated table (in particular ), which stands in contrast to @Leuz_2003.

@@

The replicated EM3 results are very similar to those of the original study, with close alignment in summary statistics and consistent identification of South Africa and Germany as the countries with the minimum and maximum EM3 values. Additionally, the replication confirms that the magnitude of firms’ accruals relative to their operating cash flows is smaller in the U.K. and the U.S. compared to Austria, Germany, and South Korea, consistent with the original findings.
